A Case Study on Abstractions to Converge High-Throughput and High-Performance Computing

### 2017-03-20 abstract.tex
Reduce stub abstract to 150 words required by SC

Experiments at the Large Hadron Collider (LHC) face unprecedented computing
challenges. Heterogeneous resources are distributed worldwide, thousands of
physicists analyzing the data need remote access to hundreds of computing
sites, the volume of processed data is beyond the exabyte scale, and data
processing requires more than billions of hours of computing usage per year. The
PanDA (Production and Distributed Analysis) system was developed to meet the
scale and complexity of LHC distributed computing for the ATLAS experiment. In
the process, the old batch job paradigm of computing in HEP was discarded in
favor of a far more flexible and scalable model. The success of PanDA at the LHC
is leading to widespread adoption and testing by other experiments. PanDA is
the first exascale workload management system in HEP, already operating at
a million computing jobs per day, and processing over an exabyte of data in
2013. We will describe the design and implementation of PanDA, present data on
the performance of PanDA at the LHC, and discuss plans for future evolution
of the system to meet new challenges of scale, heterogeneity and increasing
user base.

>>>>

% Experiments at the Large Hadron Collider (LHC) face unprecedented computing
% challenges. Heterogeneous resources are distributed worldwide, thousands of
% physicists analyzing the data need remote access to hundreds of computing
% sites, the volume of processed data is beyond the exabyte scale, and data
% processing requires more than billions of hours of computing usage per year. The
% PanDA (Production and Distributed Analysis) system was developed to meet the
% scale and complexity of LHC distributed computing for the ATLAS experiment. In
% the process, the old batch job paradigm of computing in HEP was discarded in
% favor of a far more flexible and scalable model. The success of PanDA at the LHC
% is leading to widespread adoption and testing by other experiments. PanDA is
% the first exascale workload management system in HEP, already operating at
% a million computing jobs per day, and processing over an exabyte of data in
% 2013. We will describe the design and implementation of PanDA, present data on
% the performance of PanDA at the LHC, and discuss plans for future evolution
% of the system to meet new challenges of scale, heterogeneity and increasing
% user base.

Experiments at the Large Hadron Collider (LHC) face unprecedented computing
challenges. Thousands of physicists analyze exabytes of data every year, using
billions of computing hours on hundreds of computing sites worldwide. PanDA
(Production and Distributed Analysis) is a workload management system (WMS)
developed to meet the scale and complexity of LHC distributed computing for the
ATLAS experiment. PanDA is the first exascale workload management system in HEP,
executing millions of computing jobs per day, and processing over an exabyte of
data in 2016. In this paper, we introduce the design and implementation of
PanDA, describing its deployment on Titan, the third biggest supercomputer in
the world. We analyze scalability, reliability and performance of PanDA on
Titan, highlighting the challenges addressed by its architecture and
implementation. We present preliminary results of experiments performed with the
Next Generation Executer, a prototype we developed to meet new challenges of
scale and resource heterogeneity.
